### 2024-09-23 Manuscript/main_ecography_R1.tex
R1 version INIT

\noindent {\normalsize \sc
Thomas Guillerme$^{1,*}$, 
Pedro Cardoso$^{2,3}$, %pedro.cardoso@helsinki.fi
% Carlos P. Carmona$^{4}$,
Maria Wagner J\o rgensen$^{4}$, %mwj207@student.bham.ac.uk
Stefano Mammola$^{3,5,6}$, %stefanomammola@gmail.com
Thomas J. Matthews$^{4,7}$}\\ % txm676@gmail.com
\noindent {\small \it 
$^1$School of Biosciences, The University of Sheffield, Sheffield, S10 2TN, United Kingdom.\\
$^2$CE3C—Centre for Ecology, Evolution and Environmental Changes, CHANGE – Global Change and Sustainability Institute, Faculty of Sciences, University of Lisbon, Lisbon, Portugal\\
$^3$Laboratory for Integrative Biodiversity Research (LIBRe), Finnish Museum of Natural History (Luomus), University of Helsinki, Helsinki, Finland\\
% $^4$Institute of Ecology and Earth Sciences, University of Tartu, Tartu, Estonia\\
$^4$School of Geography, Earth and Environmental Sciences and Birmingham Institute of Forest Research, University of Birmingham, Birmingham B15 2TT, UK\\
$^5$Molecular Ecology Group (MEG), Water Research Institute, National Research Council (CNR-IRSA), Verbania Pallanza, Italy\\
$^6$National Biodiversity Future Center, Piazza Marina 61, 90133 Palermo, Italy\\
$^7$Centre for Ecology, Evolution and Environmental Changes/Azorean Biodiversity Group / CHANGE – Global Change and Sustainability Institute and Universidade dos Açores – Faculty of Agricultural Sciences and Environment; PT-9700-042, Angra do Hero\'ismo, A\c ores, Portugal.\\}

\end{center}
\bigskip
\noindent{*\bf Corresponding author.} \textit{t.guillerme@sheffield.ac.uk}\\

\begin{itemize}
   \item Article type: Letter
   \item Number of words in the abstract: 189
   \item Number of words in the main text: 3960
   \item Number of words in the text box: 419
   \item Number of references: 54
   \item 3 Figures, 2 tables and 1 text box
\end{itemize}

\subsection{Statement of authorship}

TG, PC, MWJ, SM and TJM designed the study, analysed the data and wrote the manuscript. TG wrote the code to analyse the data.

\subsection{Data accessibility statement}

All code and data required to reproduce this analysis is available on GitHub: \url{https://github.com/TGuillerme/eco_metrics_simulations/}.

%---------------------------------------------
%
%       ABSTRACT
%
%---------------------------------------------

@@

\section{Acknowledgements}
Thanks to Andrew Beckerman, Natalie Cooper, Alain Danet, Thomas Johnson and Gavin Thomas for comments on early versions of this manuscripts.
TG was funded by the UKRI-NERC grant NE/X016781/1.
SM was supported by NBFC, funded by the Italian Ministry of University and Research, PNRR, Missione 4, Componente 2, ``Dalla ricerca all'impresa'', Investimento 1.4, Project CN00000033.
MWJ was supported by NERC CENTA2 grant NE/S007350/1 and University of Birmingham.

>>>>

% \noindent {\normalsize \sc
% Thomas Guillerme$^{1,*}$, 
% Pedro Cardoso$^{2,3}$, %pedro.cardoso@helsinki.fi
% % Carlos P. Carmona$^{4}$,
% Maria Wagner J\o rgensen$^{4}$, %mwj207@student.bham.ac.uk
% Stefano Mammola$^{3,5,6}$, %stefanomammola@gmail.com
% Thomas J. Matthews$^{4,7}$}\\ % txm676@gmail.com
% \noindent {\small \it 
% $^1$School of Biosciences, The University of Sheffield, Sheffield, S10 2TN, United Kingdom.\\
% $^2$CE3C—Centre for Ecology, Evolution and Environmental Changes, CHANGE – Global Change and Sustainability Institute, Faculty of Sciences, University of Lisbon, Lisbon, Portugal\\
% $^3$Laboratory for Integrative Biodiversity Research (LIBRe), Finnish Museum of Natural History (Luomus), University of Helsinki, Helsinki, Finland\\
% % $^4$Institute of Ecology and Earth Sciences, University of Tartu, Tartu, Estonia\\
% $^4$School of Geography, Earth and Environmental Sciences and Birmingham Institute of Forest Research, University of Birmingham, Birmingham B15 2TT, UK\\
% $^5$Molecular Ecology Group (MEG), Water Research Institute, National Research Council (CNR-IRSA), Verbania Pallanza, Italy\\
% $^6$National Biodiversity Future Center, Piazza Marina 61, 90133 Palermo, Italy\\
% $^7$Centre for Ecology, Evolution and Environmental Changes/Azorean Biodiversity Group / CHANGE – Global Change and Sustainability Institute and Universidade dos Açores – Faculty of Agricultural Sciences and Environment; PT-9700-042, Angra do Hero\'ismo, A\c ores, Portugal.\\}

\end{center}
% \bigskip
% \noindent{*\bf Corresponding author.} \textit{t.guillerme@sheffield.ac.uk}\\

% \noindent (Keywords: Functional diversity, dissimilarity, disparity, patterns, processes, mechanisms)\\

% \begin{itemize}
%    \item Article type: Perspective
%    \item Number of words in the abstract: 189
%    \item Number of words in the main text: 3960
%    \item Number of words in the text box: 419
%    \item Number of references: 54
%    \item 3 Figures, 2 tables and 1 text box
% \end{itemize}

% \subsection{Statement of authorship}

% TG, PC, MWJ, SM and TJM designed the study, analysed the data and wrote the manuscript. TG wrote the code to analyse the data.

% \subsection{Data accessibility statement}

% All code and data required to reproduce this analysis is available on GitHub: \url{https://github.com/TGuillerme/eco_metrics_simulations/}.

% %---------------------------------------------
% %
% %       ABSTRACT
% %
% %---------------------------------------------

@@

% \section{Acknowledgements}
% Thanks to Andrew Beckerman, Natalie Cooper, Alain Danet, Thomas Johnson and Gavin Thomas for comments on early versions of this manuscripts.
% TG was funded by the UKRI-NERC grant NE/X016781/1.
% SM was supported by NBFC, funded by the Italian Ministry of University and Research, PNRR, Missione 4, Componente 2, ``Dalla ricerca all'impresa'', Investimento 1.4, Project CN00000033.
% MWJ was supported by NERC CENTA2 grant NE/S007350/1 and University of Birmingham.
